Software Ticket Quality

### 2017-10-30 proposal/mprop.tex
Clean up bib file
Add paper on information quality

>>>>

 \textbf{AIMQ}\cite{lee2002aimq}:
 \begin{itemize}
   \item \textbf{What were the goals?}
     The main challenge set by the authors was to develop an overall model
     with an accompanying assessment instrument for quantifying information
     quality.
   \item \textbf{What was the method?}
     They developed a methodology called AIM quality (hence the name AIMQ) which
     they applied at 5 different organizations. It has 3 main components:
      \begin{itemize}
        \item 2 $\times$ 2 model of what information quality means to managers;
        \item questionnaire for measuring information quality along the dimensions
          found in first step;
        \item two analysis techniques for interpreting the assessments captured 
          by the questionnaire.
      \end{itemize} 
   \item \textbf{What did they learn?}
      They conclude that the AIMQ methodology proved to be a practical information
      quality tool to organizations.
   \item \textbf{Relevance to our work}: the paper gave us valuable insight into 
     how to assess information quality.
\end{itemize}
